Percussive Synthesizer Generation with Virtual Listeners

### 2020-08-22 templates_aimusic2020/paper.tex
Updates from Overleaf

\section{Building and Evaluating The System}
% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
Ear Type / System Name & Drop Rule         & Size & HvH  & H+FC & H+CNN & H+E/F & H+MEM \\ \hline
\multirow{2}{*}{TPE} & No Drops          & 257  & 0.37 & 0.35 & 0.36  & 0.36  &       \\ \cline{2-8} 
                     & Bads and Others   & 154  & 0.47 & 0.59 & 0.54  & 0.50  &       \\ \hline
\multirow{2}{*}{MEM} & No Drops          & 300  & 0.34 &      &       &       & 0.25  \\ \cline{2-8} 
                     & All Bad and Other & 120  & 0.62 &      &       &       & 0.59  \\ \hline
\end{tabular}

@@

\textbf{Conclusion:} We successfully built a generative system for creation of percussive sounds via automatic programming of virtual synthesizers. We verified its results with human listeners.
Our work enables not only the creation of new libraries of percussion sounds, but new synthesizer programs which can be modified and studied. 
Manual listening tests revealed much room for improvement, particularly with accurate separation of percussive sounds from the infinitely large set of non-percussive sounds. We had some success in our utilization of latent representations of autoencoder networks as low-dimensional representations of short sound files. \\ 
\textbf{Threats to Validity:} The lack of consistency in training and accuracy measurements makes comparisons between TPEs and MEMs difficult. Many arbitrary design decisions have been made, particularly in the design of our TPE classifiers and selection of datasets for training and testing. We cannot quantify the novelty of our results. Our requirement for training data remains high. \\
\textbf{Future Work:} Effective implementation of few-shot learning is a priority. Program generation can be improved by reinforcement learning and other heuristics.

@@

\begin{appendices}
%======================
\chapter{Datasets Details and Downloads}
\label{appendix:datasets}
\subsection{Download Instructions}
FreeDB, survey data, and randomly generated sounds can be downloaded from: \url{https://zenodo.org/record/3994999}\\
RadarDB requires lengthy downloads and processing. The script for its automated creation can be found under the \enquote{getting\_data} directory of our project code: \footnote{\url{https://github.com/imilas/Synths_Stacks_Search}}
\subsection{Details}
Our data sources are a large set of 2 second or shorter drum samples aggregated from personal libraries, free drum kits from the sample-swap project \footnote{https://sampleswap.org/} which we organized into 5 groups, and a large set of drum sounds aggregated from royalty free sources such as music radar \footnote{https://www.musicradar.com/}. We put together 3 databases of drums using these sources. We also created a database of synthetic noise from 1, 3, and 5 stacked virtual synthesizers. Specifications about our datasets can be found in tables~\ref{db:self},~\ref{db:radar},~\ref{db:sampleswap} and~\ref{db:noise}. We have made our dataset of free-drum sounds available for download. The scripts used to download and process royalty free samples are also made available.

>>>>

\section{Building and Evaluating The System}
% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
Ear Type / System Name & Drop Rule         & Size & HvH  & H+FC & H+CNN & H+E/F & H+MEM \\ \hline
\multirow{2}{*}{TPE} & No Drops          & 257  & 0.37 & 0.35 & 0.36  & 0.36  &       \\ \cline{2-8} 
                     & All Bad and Other   & 154  & 0.47 & 0.59 & 0.54  & 0.50  &       \\ \hline
\multirow{2}{*}{MEM} & No Drops          & 300  & 0.34 &      &       &       & 0.25  \\ \cline{2-8} 
                     & All Bad and Other & 120  & 0.62 &      &       &       & 0.59  \\ \hline
\end{tabular}

@@

\textbf{Conclusion:} We successfully built a generative system for creation of percussive sounds via automatic programming of virtual synthesizers. We verified its results with human listeners.
Our work enables not only the creation of new libraries of percussion sounds, but new synthesizer programs which can be modified and studied. 
Manual listening tests revealed much room for improvement, particularly with accurate separation of percussive sounds from the infinitely large set of non-percussive sounds. We had some success in our utilization of latent representations of autoencoder networks as low-dimensional representations of short sound files. \\ 
\textbf{Threats to Validity:} The lack of consistency in training and accuracy measurements makes comparisons between TPEs and MEMs difficult. Many arbitrary design decisions have been made, particularly in the design of our TPE classifiers and selection of datasets for training and testing. We cannot quantify the novelty of our results. Our requirement for training data remains high. \\
\textbf{Future Work:} Effective implementation of few-shot learning is a priority. Program generation may be improved by reinforcement learning and other heuristics.

@@

\begin{appendices}
%======================
\chapter{Datasets, Details, and Downloads}
\label{appendix:datasets}
\subsection{Download Instructions}
FreeDB, survey data, and randomly generated sounds can be downloaded from: \url{https://zenodo.org/record/3994999}\\
RadarDB requires lengthy downloads and processing. The script for its automated creation can be found under the \enquote{getting\_data} directory of our project code: \footnote{\url{https://github.com/imilas/Synths_Stacks_Search}}
\subsection{Details}
Our data sources are a large set of 2 second or shorter drum samples aggregated from personal libraries, free drum kits from the sample-swap project \footnote{https://sampleswap.org/} which we organized into 5 groups, and a large set of drum sounds aggregated from royalty free sources such as music radar \footnote{https://www.musicradar.com/}. We put together 3 databases of drums using these sources. We also created a database of synthetic noise from 1, 3, and 5 stacked virtual synthesizers. Specifications about our datasets can be found in tables~\ref{db:self},~\ref{db:radar},~\ref{db:sampleswap} and~\ref{db:noise}. We have made our dataset of free-drum sounds available for download. The scripts used to download and process royalty free samples are also made available.
